### 2014-06-06 paper/body.tex
small change

Because finding Gabor features on the first layer seems to occur regardless of the exact cost function and natural image dataset used, we may call these these features \emph{general}. On the other hand, we know that the last layer of a trained network will depend greatly on the chosen \{network model, dataset\} combination. For example, for networks trained toward a supervised classification objective, each output unit will be specific to a particular class, at least to the extent that training is successful. In this sense, let's say that the last layer features are \emph{specific}. So far these terms are only intuitively defined, but we shall provide a candidate for a more rigorous definition below. \todo{Consider something like: ``Empirically, we know that these filter are generic because they can be transferred to other networks and perform well [cites]. Transferring information learned on one task or dataset to a new task or data set is know as \emph{Transfer Learning} [cites].''}

If these Gabor features of the first features are general, and the features of the last layer are specific, there must be a transition from general to specific somewhere in the network. This observation raises a few questions:

\begin{itemize}
	\item Can we quantify the degree to which a particular layer is general or specific?
	\item For a particular deep network, does the transition occur suddenly from layer $n$ to $n+1$, or is it spread out over several layers?
	\item Where does this transition take place: near the bottom, middle, or top of the network?
\end{itemize}

Once one has general features from some layer of a base network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task. The process that is usually followed is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second task. When following this path, one can choose to backpropagate the errors from the new task into the base features to \emph{fine-tune} them to the new task, or they can be left frozen. In cases where the second dataset is smaller than the first, fine-tuning the base features may result in overfitting, so the features are often left frozen. On the other hand, if the second dataset is large enough, the base features can be fine-tuned to the new task. Of course, if the second dataset is very large, there would be no need to transfer because the base filters could just be learned from scratch. These two domains --- fine-tuned features or frozen features --- are distinct and are compared later.

>>>>

Because finding Gabor features on the first layer seems to occur regardless of the exact cost function and natural image dataset used, we may call these these features \emph{general}. On the other hand, we know that the last layer of a trained network will depend greatly on the chosen \{network model, dataset\} combination. For example, for networks trained toward a supervised classification objective, each output unit will be specific to a particular class, at least to the extent that training is successful. In this sense, let's say that the last layer features are \emph{specific}. So far these terms are only intuitively defined, but we shall provide a candidate for a more rigorous definition below. 
If these Gabor features of the first features are general, and the features of the last layer are specific, there must be a transition from general to specific somewhere in the network. This observation raises a few questions:

\begin{itemize}
	\item Can we quantify the degree to which a particular layer is general or specific?
	\item For a particular deep network, does the transition occur suddenly at a single layer, or is it spread out over several layers?
	\item Where does this transition take place: near the bottom, middle, or top of the network?
\end{itemize}

Once one has general features from some layer of a base network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task \todo{cites}. The process that is usually followed is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second task. When following this path, one can choose to backpropagate the errors from the new task into the base features to \emph{fine-tune} them to the new task, or they can be left frozen. In cases where the second dataset is smaller than the first, fine-tuning the base features may result in overfitting, so the features are often left frozen. On the other hand, if the second dataset is large enough, the base features can be fine-tuned to the new task. Of course, if the second dataset is very large, there would be no need to transfer because the base filters could just be learned from scratch. These two domains --- fine-tuned features or frozen features --- are distinct and are compared later.
